Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-09-12 smt/response.tex

\documentclass[12pt]{article}
\usepackage{a4wide,url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}

\begin{document}
\section*{Response Letter}
We are grateful to the reviewers for their time, effort, and constructive remarks.
All remarks have been accounted for in the revised version, as detailed in our response below.

\section*{Reviewer 2}
Our response in \textcolor{blue}{blue} follows the corresponding remark from the reviewer in \textcolor{red}{red}.

\begin{itemize}
\item \textcolor{red}{The abstract should be shorter.} \textcolor{blue}{
We have revised the abstract, and reduced its length from 22 to 15 lines.
}
\item \textcolor{red}{The literature review has not been organized in a proper format. The references are so old. New related works need to be explained. The authors should use a separate Section for this purpose and compare the novelty of the present approach with them.} \textcolor{blue}{
Following the recommendation of the reviewer, we have reorganized the literature review, and devoted a new section (Section 2 in the revised manuscript)
to this topic. We have also included a review of more recent and relevant literature (references \cite{bein10, bhukya14}).
In Section 1.2, we now state explicitly the contributions from the present work, and explain how they relate to the current literature.
}
\item \textcolor{red}{They also should consider a separate section on the network model and assumptions.} \textcolor{blue}{
We have restructured the former Section 2 (now Section 3) into three subsections.
The first is devoted to mathematical notation and underlying assumptions, the second addresses the network model,
while the problem definition is given in the third subsection.
}
\item \textcolor{red}{The diagrams of figures are not distinguishable in black and white print. The legends should be corrected.} \textcolor{blue}{
While paying particular attention to their appearance in black and white print, we have given all figures,
including their legends, a complete overhaul.
}
\item \textcolor{red}{All equations should be terminated with "." or "," as well as sentences.} \textcolor{blue}{
Done.
}
\item \textcolor{red}{The legends, markers and other details of the figures are so small.} \textcolor{blue}{
Legends, markers, and other details are now given in larger size.
}
\item \textcolor{red}{A fundamental weak point is that there are no numerical results comparing the proposed scheme with the other new works;} \textcolor{blue}{
We agree that a comparison with alternative contemporary methods largely benefits the paper.
To that end, we have included a comparison with an adapted metaheuristic algorithm based on iterative combination of elite solutions \cite{pajor18}.
The method is described along with presentatin of results from the experiments in the new Section 7.3.
}
\item \textcolor{red}{The simulation graphs need more expiation and justification.} \textcolor{blue}{
For better justification of the numerical results illustrated graphically in the former Section 6 (now Section 7),
we have added more explanations.
}
\item \textcolor{red}{ The main aim of this paper is the energy, How is the energy issue modeled? Why is not the real models used in the paper?} \textcolor{blue}{
In the new Section 3.2 on the network model, we now explain more detailed how the energy is modeled.
Justification is added in terms of references to relevant and frequently cited works (see [?], ....).
}
\item \textcolor{red}{Overall the novelty of the proposed approach in unclear and the paper is hard to follow
The authors have not considers the wireless problems in the paper.} \textcolor{blue}{
The novelty of and the contributions from the paper are now explicitly stated in Section 2.
We also explain how the paper relates to other works on energy minimization in wireless networks.
}
\end{itemize}

@@

\section*{Reviewer 3}
Our response in \textcolor{blue}{blue} follows the corresponding remark from the reviewer in \textcolor{red}{red}.

\begin{itemize}
\item \textcolor{red}{The paper provides two new ILP formulations for the Shared Multicast Tree (SMT) problem in wireless ad hoc networks.
To address the problem of ILP scalability, the paper also provides a study and proofs of related theorems that shed light on the quality of
solutions achievable by  LP  bounds.
As the number and also provides a new constraint generation scheme.
Numerical results demonstrate the usefulness of the approach. The paper is well written.} \textcolor{blue}{
We are grateful to the reviewer for her/his encouraging remarks, and we appreciate the (s)he finds the paper well written.
}
\item \textcolor{red}{Overall, the methodology makes contribution in the field of optimization as the approach can be used to address other similar problems
that can be modeled as ILP which is not scalable.
However, this paper aims to address the problem of SMT in wireless ad hoc networks and it is
really motivated by the important problem of saving energy in sensor networks.
There I see a certain minor weakness.
The model considered ignores details of energy consumption is sensor network
(see for example Halgamuge et al., Progress in Electromagnetics Research, 12, 2009, or other sources).
It will be good to my opinion to point out this weakness and provide certain qualitative comments to benefit the practitioners,
on how the work can be used in practice, or what is still needed to be done so the work can be useful.} \textcolor{blue}{
We thank the reviewer for suggesting this very useful reference, a citation of which has been included in the revised version of the paper.
We fully agree that there are gaps between the coarse energy model applied in our work and more detailed energy models for energy consumption is sensor networks,
e.g.\ those analyzed in \cite{halgamuge}.
These gaps, and their possible implications on practical usability of our approaches, are now discussed in the new Section 3.2.
}
\end{itemize}

@@

\noindent
Final comment: We thank the reviewers again for their constructive remarks, which largely helped us to improve the presentation of our findings.

\begin{thebibliography}{}

\bibitem{bein10}
Bein D, Zheng SQ (2010)
Energy efficient all-to-all broadcast in all-wireless networks.
Information Sciences 180(10):1781--1792

\bibitem{bhukya14}
Bhukya WN, Singh A (2014)
\emph{p}-shrink: A Heuristic for Improving Minimum All-to-All Power Broadcast Trees in Wireless Networks.
In: Proceedings of Ninth International Conference on Wireless Communication and Sensor Networks 2014 
Vol.\ 299, pp 61--69

\bibitem{halgamuge}
Halgamuge MN, Zukerman M, Ramamohanarao K (2009)
An estimation of sensor energy consumption.
Progress In Electromagnetics Research B 12:259--295

\bibitem{pajor18}
Pajor T, Uchoa E, Werneck RF (2018)
A robust and scalable algorithm for the Steiner problem in graphs.
Math Prog Comp 10:69--118

\end{thebibliography}
\end{document}

### 2018-09-12 smt/ivanova.tex
MI: (SMT) Added a reference (Guo and Yang), newly written text is now in a blue font. Old text that is moved to different sections/paragraphs remains black
MI (SMT): Addressed the criticism of Reviewer 2 and added more explanation to the graphs in Fig. 3. Also updated the response letter accordingly.
MI (SMT): Added two references that might address the complain 'too old references'. There is a new Section 7.3 devoted to the description of the meta heuristic algorithm from [Pajor et Al. (2018)] and prepared writing about the experiments planned with this method. The response letter is updated

\bibitem[Bauer et al.(2008)]{bauer08}
Bauer J, Haugland D, Yuan D (2008)
Analysis and computational study of several integer programming formulations for minimum-energy multicasting in wireless ad hoc networks.
Networks 52(2):57–68

@@

@@

\bibitem[Montemanni and Leggieri(2011)]{montemanni11}
Montemanni R, Leggieri V (2011)
A branch and price algorithm for the minimum power multicasting problem in wireless sensor networks.
Math Meth Oper Res
74:327--342

>>>>

\bibitem[Bauer et al.(2008)]{bauer08}
Bauer J, Haugland D, Yuan D (2008)
Analysis and computational study of several integer programming formulations for minimum-energy multicasting in wireless ad hoc networks.
Networks 52(2):57–68
\textcolor{blue}{\bibitem[Bein and Zheng(2010)]{bein10}
Bein D, Zheng SQ (2010)
Energy efficient all-to-all broadcast in all-wireless networks.
Information Sciences 180(10):1781--1792}
\textcolor{blue}{\bibitem[Bhukya and Singh(2014)]{bhukya14}
Bhukya WN, Singh A (2014)
\emph{p}-shrink: A Heuristic for Improving Minimum All-to-All Power Broadcast Trees in Wireless Networks.
In: Proceedings of Ninth International Conference on Wireless Communication and Sensor Networks 2014 
Vol.\ 299, pp 61--69}

@@

\bibitem[Guo and Yang(2004)]{guo}
Guo S, Yang O (2004)
Minimum Energy Multicast Routing for Wireless Ad-hoc Networks with Adaptive Antennas 
In: Proceedings of the 12th IEEE International Conference on Network Protocols ICNP 2004,
pp 151--160

@@

\bibitem[Montemanni and Leggieri(2011)]{montemanni11}
Montemanni R, Leggieri V (2011)
A branch and price algorithm for the minimum power multicasting problem in wireless sensor networks.
Math Meth Oper Res
74:327--342
\textcolor{blue}{\bibitem[Pajor et al.(2018)]{pajor18}
Pajor T, Uchoa E, Werneck RF (2018)
A robust and scalable algorithm for the Steiner problem in graphs.
Math Prog Comp 10:69--118
}

### 2018-09-12 smt/sec2-literature.tex
MI (SMT): Added two references that might address the complain 'too old references'. There is a new Section 7.3 devoted to the description of the meta heuristic algorithm from [Pajor et Al. (2018)] and prepared writing about the experiments planned with this method. The response letter is updated accordingly, and now it seems almost complete, the only thing that I really cannot figure out is how to respond to the complaint about the absent contribution. So far I only created a separate section with a clear title, but I don't know how to explain the contribution more

>>>>

\textcolor{blue}{\citet{bein10} study energy efficiency in wireless networks where all nodes can initiate a message, and the communicatin takes place in a single all-to-all broadcast tree.
A heuristic algorithm generating all-to-all broadcast trees is proposed in \citet{bhukya14}, along with an experimental evaluation confirming its merit.}

### 2018-09-12 smt/sec6-exp.tex
MI (SMT): Added two references that might address the complain 'too old references'. There is a new Section 7.3 devoted to the description of the meta heuristic algorithm from [Pajor et Al. (2018)] and prepared writing about the experiments planned with this method. The response letter is updated accordingly, and now it seems almost complete, the only thing that I really cannot figure out is how to respond to the complaint about the absent contribution. So far I only created a separate section with a clear title, but I don't know how to explain the contribution more

>>>>

\textcolor{blue}{\subsection{Comparison with alternative methods}}

\textcolor{blue}{
To the best of our knowledge, SMT has not been studied extensively in terms of inexact methods.
However, there is a manifold of a thorough research of the minimum Steiner tree problem, with the possibility of adapting the methods on SMT.
We turn our attention to recently pusblished paper \citet{pajor18} which notains a metaheuristic algorithm for a fast generation of good solution to the Steiner tree problem.
The method is general, and is therefore very suitable for adaptation to our purposes.
The high level description is as follows:}
\begin{algorithm}
\textcolor{blue}{
Create an empty pool $P$ of elite solutions with capacity $\gamma=\left\lceil\sqrt{M/2}\right\rceil$\;
\For {$i\in \{1,\dots,M$\}} {
Generate a new solution $S$ using a constructive algorithm, local search, and randomization\;
\If {$i<\gamma$} {$P\leftarrow P\cup \{S\}$}
\Else {
$\hat{S}\leftarrow\arg\max_{S'\in P} c(S')$\;
\If {$c(\hat{S})> c(S)$}{$P\leftarrow P\cup \{S\}\setminus\{\hat{S}\}$}
$\hat{S}\leftarrow\arg\max_{S'\in P} c(S')$\;
Generate a solution $\tilde{S}$ by combining $S$ with solutions in $P$\;
\If {$c(\hat{S})> c(\tilde{S})$}{$P\leftarrow P\cup \{\tilde{S}\}\setminus\{\hat{S}\}$}
}
}
\Return $\arg\min_{S'\in P} c(S')$\;
 \caption{Outline of the metaheuristic algorithm}
}
\label{alg:meta}
\end{algorithm}
\textcolor{blue}{The construction procedure and local search is the adapted BIP algorithm together with refinements presented in \citet{ivanova16isco}.
The remaining parts of the algorithm are carried out as discussed in \citet{pajor18}.
The randomization is achieved by perturbing the edge costs in the input graph.
The obtained solution $S$ is evaluated with respect to the real (original) edge costs and added to the pool $P$ if the pool capacity is not filled.
If the pool is full and its worst solution $\hat{S}$ is worse than $S$, $\hat{S}$ is replaced by $S$ in $P$.
Then a new solution $\tilde{S}$ is constructed by combining some solution in $P$ with $S$. 
First, we adjust edge costs resulting in a modified input instance, 
and then run the construction and local search yielding $\tilde{S}$.
This new solution is again added to the pool if it is better than some solution already in $P$.
The adjustment of the edges tries to promote edges that appear in both $S$ and a selected solution in $P$. 
In that case, the original cost is preserved.
If an edge is present in only one of the two solutions, its cost is multiplied by a random integer between 100 and 500.
If an edge appears in neither of the solutions, its edge is multiplied by 1000, which makes it very unlikely to appear in the result $\tilde{S}$ of the combination.
}
\begin{table}[]
\centering
\textcolor{blue}{
\begin{tabular}{rrrrrrrrrrr}
\multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{3}{c}{5 min}  & \multicolumn{3}{c}{10 min} & \multicolumn{3}{c}{20 min}     \\\hline
\multicolumn{1}{l}{$|V|$} & \multicolumn{1}{l}{$|D|$} & \multicolumn{1}{l}{$\mathcal{X}_1$} & \multicolumn{1}{l}{$\mathcal{F}_1$} & \multicolumn{1}{l}{$\mathcal{M}$} & \multicolumn{1}{l}{$\mathcal{X}_1$} & \multicolumn{1}{l}{$\mathcal{F}_1$} & \multicolumn{1}{l}{$\mathcal{M}$} & \multicolumn{1}{l}{$\mathcal{X}_1$} & \multicolumn{1}{l}{$\mathcal{F}_1$} & \multicolumn{1}{l}{$\mathcal{M}$} \\\hline
20  & 10   &     &   &   &   &    &    &    &    &       \\
22  & 11   &     &   &   &   &    &    &    &    &       \\
24  & 12   &     &   &   &   &    &    &    &    &                                  
\end{tabular}
}
\caption{\textcolor{blue}{Comparison of the metaheuristic algorithm and solving IP models with imposed time-limit.}}
\label{tab:metamod}
\end{table}

\textcolor{blue}{
Tab.\ref{tab:metamod} summarizes the comparison of the metaheuristic algorithm with the ability of IP models to produce feasible solutions when restricted time limit.
Each column represents the average percentage of objective function of the best method in a given instance.
The averages are calculated over all instances of given $V$ and $D$.
}

\textcolor{blue}{
The resulting values reveal that...
}
